---
title: "Defining parameters as functions of other parameters"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Defining parameters as functions of other parameters}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In some cases, users may not wish to provide a parameter value, but rather have a value calculated based on other parameters. Currently, the only parameters that can be provided as functions are:

- `nu_constant` in `constants()`
- `sh_constant` in `constants()`
- `T_sky` in `enviro_par()`

I plan to make more of these in the future, but I'll briefly demonstrate how one would change the `T_sky` function. The default function from [Okajima *et al.* (2012)](https://doi.org/10.1007/s11284-011-0905-5), which was hard-coded in versions 1.0.0 and 1.0.1, is:

```{r}

library(tealeaves)

leaf_par   <- make_leafpar()   # leaf parameters
enviro_par <- make_enviropar() # environmental parameters
constants  <- make_constants() # physical constants

enviro_par$T_sky

```

Let's change it simply be the air temperature (`T_air`). The current requirements for this function as of version 1.0.2 are:

- It must take `pars` as the only argument, where `pars` is the concatenated set of leaf (`leaf_par()`) and environmental parameters (`enviro_par()`)
- It must return `T_sky` in units K. You can ensure this by using `units::set_units(., K)`

```{r}

enviro_par <- make_enviropar(
  replace = list(T_sky = function(pars) {pars$T_air})
)
enviro_par$T_sky

T_leaf <- tleaf(leaf_par, enviro_par, constants, quiet = TRUE)

knitr::kable(T_leaf)

```
