---
title: "{tealeaves} for Intermediate Users"
author: "Chris Mur"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(dplyr)
library(ggplot2)
library(magrittr)
library(tealeaves)

```

blah

```{r, eval = FALSE, echo = TRUE}

# install tidyverse if necessary
# install.packages("tidyverse")

library(dplyr)
library(ggplot2)
library(magrittr)
library(tealeaves)

# Parameter sets ----

## 1. High and low light
  cs <- leafoptimizer::make_constants()
  S_sw <- leafoptimizer::ppfd2sun(set_units(c(500, 1500), "umol/m^2/s"), 
                                  set_units(0.5), 
                                  set_units(220, "kJ/mol"))

## 2. Hypo- and amphistomatous leaves
logit_sr <- set_units(c(-Inf, qlogis(0.25), 0))

## Make parameters
cs <- tealeaves::make_constants()
lp <- tealeaves::make_leafpar(
  replace = list(
    logit_sr = logit_sr
  )
)
ep <- tealeaves::make_enviropar(
  replace = list(
    S_sw = S_sw,
    T_air = set_units(seq(278.15, 313.15, length.out = 25), "K")  
    )
)

# Run tleaves ----
tl_example1 <- tleaves(lp, ep, cs)

# usethis::use_data(tl_example1)

```

```{r plot, echo = FALSE, eval = TRUE, fig.width=7}

tl_example1 %<>%
  
  # Drop units for plotting
  mutate_if(function(x) inherits(x, what = "units"), drop_units) %>%
  
  # Calculate leaf temperature differential
  mutate(dT = T_leaf - T_air) %>%
  
  # Factorize stomatal ratio 
  mutate(`Stomatal Ratio` = case_when(
    logit_sr == -Inf ~ "hypostomatous",
    logit_sr == qlogis(0.25) ~ "intermediate",
    logit_sr == 0 ~ "amphistomatous"
  )) %>%
  
  # Factorize light environment 
  mutate(Light = case_when(
    round(S_sw, 0) == 220 ~ "Shade",
    round(S_sw, 0) == 660 ~ "Sun"
  ))

ggplot(tl_example1, aes(T_air, dT, color = `Stomatal Ratio`)) +
  facet_grid(Light ~ .) + 
  geom_line() +
  theme_minimal() + 
  NULL

```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
